OptiFit: an improved method for fitting amplicon sequences to existing OTUs

### 2021-12-15 paper/paper.Rmd
Allow paper to be knitted outside snakemake

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE}
schtools::set_knitr_opts()
#knitr::opts_knit$set(base.dir = here::here(),
#                     base.url = "../")
knitr::opts_chunk$set(fig.path = 'figures/',
                      dpi = 300)
```

@@

figures_meta <- yaml::read_yaml(here('paper', 'figures.yaml'))

figs <- function(fig_name, attribute, include_figures = params$include_figures) {
  value <- figures_meta[[fig_name]][[attribute]]
  if (attribute == 'cap') {
    value <- glue("\\label{fig:[fig_name]}[value]", .open='[', .close = ']')
  } else if (attribute == 'dim' & !isTRUE(include_figures)) {
    value <- c(0.1,0.1)
  } else {
    value <- eval(parse(text = value))
  }
  return(value)
}

render_figure <- function(fig_name, include_figures = params$include_figures) {
  if (isTRUE(include_figures)) {
    figs(fig_name, 'path') %>%
      tiff::readTIFF() %>%
      grid::grid.raster()
  } else {
    ggplot() + theme_void()
  }
}

@@

```{r algorithm, fig.dim=figs('algorithm','dim'), fig.cap=figs('algorithm','cap')}
render_figure('algorithm')
```

@@

```{r workflow, fig.dim=figs('workflow', 'dim'), fig.cap=figs('workflow','cap')}
render_figure('workflow')
```

@@

```{r results_sum, fig.dim=figs('results_sum', 'dim'), fig.cap=figs('results_sum', 'cap')}
render_figure('results_sum')
```

@@

```{r results_split, fig.dim=figs('results_split', 'dim'), fig.cap=figs('results_split', 'cap')}
render_figure('results_split')
```

```{r assert_split_fracs, include = FALSE}
close_enough(cv_fit_split_mcc_human_simple, 0, tol = 10^-3)
assert_that(sec_fit_split_human_simple_1 > sec_fit_split_human_simple_9)
assert_that(frac_fit_split_human_simple_1 < frac_fit_split_human_simple_9)
```

>>>>

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE}
schtools::set_knitr_opts()
knitr::opts_knit$set(base.dir = here::here(), 
                     base.url = "../")
knitr::opts_chunk$set(fig.path = 'figures/',
                      dpi = 300)
```

@@

figures_meta <- yaml::read_yaml(here('paper', 'figures.yaml'))
figs <- function(fig_name, attribute) {
  value <- figures_meta[[fig_name]][[attribute]]
  if (attribute == 'cap') {
    value <- glue("\\label{fig:[fig_name]}[value]", .open='[', .close = ']')
  } else {
    value <- eval(parse(text = value))
  }
  return(value)
}

@@

```{r algorithm, eval=params$include_figures, fig.dim=figs('algorithm','dim'), fig.cap=figs('algorithm','cap')}
figs('algorithm', 'path') %>%
  tiff::readTIFF() %>%
  grid::grid.raster()
```

@@

```{r workflow, eval=params$include_figures, fig.dim=figs('workflow', 'dim'), fig.cap=figs('workflow','cap')}
figs('workflow', 'path') %>%
  tiff::readTIFF() %>%
  grid::grid.raster()
```

@@

```{r results_sum, eval=params$include_figures, fig.dim=figs('results_sum', 'dim'), fig.cap=figs('results_sum', 'cap')}
figs('results_sum', 'path') %>%
  tiff::readTIFF() %>%
  grid::grid.raster()
```

@@

```{r results_split, eval=params$include_figures, fig.dim=figs('results_split', 'dim'), fig.cap=figs('results_split', 'cap')}
figs('results_split', 'path') %>%
  tiff::readTIFF() %>%
  grid::grid.raster()
```
```{r assert_split_fracs, include = FALSE}
close_enough(cv_fit_split_mcc_human_simple, 0, tol = 10^-3)
assert_that(sec_fit_split_human_simple_1 > sec_fit_split_human_simple_9)
assert_that(frac_fit_split_human_simple_1 < frac_fit_split_human_simple_9)
```
